Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-21 paper/paper.tex
comparison

\subsubsection{Comparison with other tools}
 \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
 evolutionaries approaches to 
autonomously generate rules using the Snort IDS. They built 
their own ICMP datasets by using packet creation tools or by capturing network traffic. 
Guruprasad also used DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets 
for non-ICMP attacks.

>>>>

\subsubsection{Comparison with other tools}
 \Gui{There are a few reasons that makes the comparison between Syrius and other tools \Fix{impossible}

\textbf{Tools availability.} We tried contact with authors of 5 different papers \Fix{[10][34][37][iran][bayesian]}, but got no response from them. Since their tools are not available online or at least not publicly, we could not run them.

\textbf{Different output and specific rules.} We considered using the results they provides with results that Syrius provide, but concluded it wouldn't be possible as the results are essentially different. Commonly the  other results focus on showing the ratio of false negatives and false positives as a way to show the efficiency of the learning algorithm \Fix{citation needed}, but never comparing the generated rules to a Ground Truth, and most of times not showing individually the attacks used. Syrius' results, on the other hand, shows the generated rules that produce no false positives and negatives to the given packets, and always compares the results with a Ground Truth to verify its efficiency.

\textbf{'content' option support.} Another limitation is the support of 'content' option. Most papers do not support rule generation with the 'content' option, using only classic DDoS attacks in the rule generation, like ICMP and SYN flood, which only use numerical and categorical options. Some papers do support 'content', but don't explain well how they handle those rules with exclusive 'content'.\Fix{citation needed}}
 \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
 evolutionaries approaches to 
autonomously generate rules using the Snort IDS. They built 
their own ICMP datasets by using packet creation tools or by capturing network traffic. 
Guruprasad also used DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets 
for non-ICMP attacks.
